---
title: "hw3_yy3020"
author: "YuaoYang"
date: "2019/10/13"
output: github_document
---

```{r}
library(patchwork)
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 12,
  fig.asp = 1,
  out.width = "100%"
)

theme_set(theme_bw() + theme(legend.position = "right"))

```

# Problem 1

```{r}
data("instacart")
instacart
```
There are {`r nrow(instacart) `} observations and the structure of dataset is (`r nrow(instacart)`, `r ncol(instacart)`)in this dataset.
And the key variables are(`r colnames(instacart)`).  The fisrt row means the identifier is {`r instacart[1,1] `}, the product identifier is {`r instacart[1,2] `}, order in which this product was added to cart is {`r instacart[1,3] `}, and  this prodcut has been ordered by this user in the past by user id {`r instacart[1,5] `}, evaluation set this order belongs in {`r instacart[1,6] `},  the order sequence number for this user is {`r instacart[1,7] `}, the day of the week on this order was placed on {`r instacart[1,8] `} day,  the hour of the day on which the order is placed on {`r instacart[1,9] `}, days since the last order is {`r instacart[1,10] `}, the name of this product is {`r instacart[1,11] `}, the aisle identifier is {`r instacart[1,12] `}  and name is {`r instacart[1,14] `}which belongs to department {`r instacart[1,15] `} and the id of this department is {`r instacart[1,13] `}.

```{r}
aisle_new = instacart%>%
  group_by(aisle) %>%
  count() %>%
  arrange(n) 
most = pull(aisle_new[134, 1])

```
There are {`r length(pull(aisle_new, aisle)) `} aisles, and the most odered item is {`r most `}.

```{r}
 instacart%>%
  group_by(aisle) %>%
  count() %>%
filter(n >10000) %>%
 ggplot(aes(x = n, y =aisle)) +
  geom_point() +
 labs(
   title = "the number of items ordered which is more than 10000",
    x = "Numbers Of Items Odered",
    y = "Aisles"
   ) 

```
From the plot, we can find that the fresh vegetablea and fresh fruits are most odered items.
```{r}
instacart %>%
  filter(aisle %in% c('baking ingredients', 'dog food care', 'packaged vegetables fruits')) %>%
select(aisle, product_name) %>%
   group_by(aisle,product_name) %>%  
  count() %>% 
   group_by(aisle)%>%
  filter(min_rank(desc(n))<=3)%>%
  knitr::kable()
 
```

#From the table, I find the most ordered items are cane sugar, light brown sugar and pure baking soda in aisle baking ingredients.The most ordered items are organix chicken & brown rice recipe, small dog biscuits and snack sticks chicken &rice recioe dog treats in aisle dog food care. The most ordered items are organic baby spinach, organic blueberries, and organic raspberries in aisle packaged vagetables fruits.




```{r}

 instacart %>%
  filter( product_name  %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
 summarise( means = mean(order_hour_of_day)) %>%
  pivot_wider(id_cols = product_name ,
              names_from = order_dow,
              values_from = means) %>%
    knitr::kable()
  
```

#From the table, I find that in Coffee Ice Cream, the mean hour is concerning on afternoon from 13 to 15, and the mean hour is concerning on noon from 11 to 14.

